Preprocessing: filtering

### 2022-09-27 analysis/baseline.Rmd
correct some comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
correct typo on filename...
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Description: This is a summary of primary analysis.

@@

```{r file, include = FALSE}
data_ioi = "preprosessor/trimmed/dt_ioi_trimmed.txt"
data_kot = "preprosessor/trimmed/dt_kot_trimmed.txt"
data_vel = "preprosessor/trimmed/dt_vel_trimmed.txt"
data_vel_diff = "preprosessor/trimmed/dt_vel_diff_trimmed.txt"
data_baseline_ioi = "preprosessor/predata/trimmed/dt_ioi_trimmed.txt"
data_baseline_kot = "preprosessor/predata/trimmed/dt_kot_trimmed.txt"
data_baseline_vel = "preprosessor/predata/trimmed/dt_vel_trimmed.txt"
data_baseline_vel_diff = "preprosessor/predata/trimmed/dt_vel_diff_trimmed.txt"
```

>>>>

Description: This is a summary of analysis comparing between baseline and test performance.

@@

```{r file, include = FALSE}
data_ioi = "preprocessor/trimmed/dt_ioi_trimmed.txt"
data_kot = "preprocessor/trimmed/dt_kot_trimmed.txt"
data_vel = "preprocessor/trimmed/dt_vel_trimmed.txt"
data_vel_diff = "preprocessor/trimmed/dt_vel_diff_trimmed.txt"
data_baseline_ioi = "preprocessor/predata/trimmed/dt_ioi_trimmed.txt"
data_baseline_kot = "preprocessor/predata/trimmed/dt_kot_trimmed.txt"
data_baseline_vel = "preprocessor/predata/trimmed/dt_vel_trimmed.txt"
data_baseline_vel_diff = "preprocessor/predata/trimmed/dt_vel_diff_trimmed.txt"
```

### 2022-09-27 analysis/both_none.Rmd
correct typo on filename...
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r file, include = FALSE}
data_ioi = "preprosessor/trimmed/dt_ioi_trimmed.txt"
data_kot = "preprosessor/trimmed/dt_kot_trimmed.txt"
data_vel = "preprosessor/trimmed/dt_vel_trimmed.txt"
data_vel_diff = "preprosessor/trimmed/dt_vel_diff_trimmed.txt"
```

>>>>

```{r file, include = FALSE}
data_ioi = "preprocessor/trimmed/dt_ioi_trimmed.txt"
data_kot = "preprocessor/trimmed/dt_kot_trimmed.txt"
data_vel = "preprocessor/trimmed/dt_vel_trimmed.txt"
data_vel_diff = "preprocessor/trimmed/dt_vel_diff_trimmed.txt"
```

### 2022-09-27 analysis/preprocessor/filtering.Rmd
correct typo on filename...
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r onset}
dt_error_onset <- checker(dt_onset, dt_ideal)

@@

@@

@@

```{r}
error_extra_onset <- fread(here("filtered/error_extra_onset.txt"))
error_extra_onset
```

@@

```{r}
error_extra_offset <- fread(here("filtered", "error_extra_offset.txt"))
error_extra_offset
```

@@

```{r}
error_missing_onset <- fread(here("filtered", "error_missing_onset.txt"))
error_missing_onset
```

@@

```{r}
error_missing_offset <- fread(here("filtered", "error_missing_offset.txt"))
error_missing_offset
```

@@

```{r}
error_sub_onset <- fread(here("filtered", "error_sub_onset.txt"))
error_sub_onset
```

@@

```{r}
error_sub_offset <- fread(here("filtered", "error_sub_offset.txt"))
error_sub_offset
```

@@

```{r}
error_ind_onset <- fread(here("filtered", "error_ind_onset.txt"))
error_ind_onset
```

@@

```{r}
# combine error
error_offset <- rbind(error_extra_offset, error_missing_offset, error_sub_offset)

@@

```{r, include = FALSE, eval = FALSE}
current_1 <- dt_onset[SubNr == error_ind_offset$SubNr[1] & TrialNr == error_ind_offset$TrialNr[1]]
current_1$RowNr <- c(1:nrow(current_1))
current_1$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_1) - nrow(dt_ideal))))
graph(current_1)

@@

```{r}
error_ind_offset <- fread(here("filtered", "error_ind_offset.txt"))
error_ind_offset
```

@@

# Checking
Check whether data look okay.

```{r, include = FALSE}
rm(list=ls(all=T)) # clear all

# read txt files
dt_correct_onset <- fread(here("filtered", "dt_correct_onset.txt"))
dt_correct_offset <- fread(here("filtered", "dt_correct_offset.txt"))
```

1) Onset
```{r}
print(checker(dt_correct_onset, dt_ideal))
```

2) Offset
```{r}
print(checker(dt_correct_offset, dt_ideal))
```

>>>>

```{r onset, echo = FALSE}
dt_error_onset <- checker(dt_onset, dt_ideal)

@@

`r nrow(dt_error_onset)` trials had at least one pitch error (`r round(nrow(dt_error_onset)/(20*16)*100, 2)` %).

@@

`r nrow(dt_error_offset)` trials had at least one pitch error (`r round(nrow(dt_error_offset)/(20*16)*100, 2)` %).

@@

```{r, echo = FALSE}
error_extra_onset <- fread(here("filtered/error_extra_onset.txt"))
error_extra_onset
```

@@

```{r, echo = FALSE}
error_extra_offset <- fread(here("filtered", "error_extra_offset.txt"))
error_extra_offset
```

@@

```{r, echo = FALSE}
error_missing_onset <- fread(here("filtered", "error_missing_onset.txt"))
error_missing_onset
```

@@

```{r, echo = FALSE}
error_missing_offset <- fread(here("filtered", "error_missing_offset.txt"))
error_missing_offset
```

@@

```{r, echo = FALSE}
error_sub_onset <- fread(here("filtered", "error_sub_onset.txt"))
error_sub_onset
```

@@

```{r, echo = FALSE}
error_sub_offset <- fread(here("filtered", "error_sub_offset.txt"))
error_sub_offset
```

@@

```{r, echo = FALSE}
error_ind_onset <- fread(here("filtered", "error_ind_onset.txt"))
error_ind_onset
```

@@

```{r, echo = FALSE}
# combine error
error_offset <- rbind(error_extra_offset, error_missing_offset, error_sub_offset)

@@

```{r, include = FALSE, eval = FALSE}
current_1 <- dt_offset[SubNr == error_ind_offset$SubNr[1] & TrialNr == error_ind_offset$TrialNr[1]]
current_1$RowNr <- c(1:nrow(current_1))
current_1$Ideal <- c(dt_ideal$Pitch, rep(NA, abs(nrow(current_1) - nrow(dt_ideal))))
graph(current_1)

@@

```{r, echo = FALSE}
error_ind_offset <- fread(here("filtered", "error_ind_offset.txt"))
error_ind_offset
```

@@

<!-- # Checking -->
<!-- Check whether data look okay. -->

<!-- ```{r, include = FALSE} -->
<!-- rm(list=ls(all=T)) # clear all -->

<!-- # set working directory -->
<!-- if (!require("here")) {install.packages("here"); require("here")} -->
<!-- here::i_am("filtering.Rmd") -->

<!-- # read functions -->
<!-- source(here("function.R")) -->

<!-- # read a text file for ideal performance -->
<!-- dt_ideal <- read.table(here("ideal.txt")) -->
<!-- colnames(dt_ideal) <- "Pitch" -->
<!-- dt_ideal$RowNr <- 1:nrow(dt_ideal) -->
<!-- setcolorder(dt_ideal, c(2, 1)) -->

<!-- # read txt files -->
<!-- dt_correct_onset <- fread(here("filtered", "dt_correct_onset.txt")) -->
<!-- dt_correct_offset <- fread(here("filtered", "dt_correct_offset.txt")) -->
<!-- ``` -->

<!-- 1) Onset -->
<!-- ```{r, echo = FALSE} -->
<!-- print(checker(dt_correct_onset, dt_ideal)) -->
<!-- ``` -->

<!-- 2) Offset -->
<!-- ```{r, echo = FALSE} -->
<!-- print(checker(dt_correct_offset, dt_ideal)) -->
<!-- ``` -->

```{r export, include = FALSE}
knitr::purl("filtering.Rmd")
```
